\documentclass[12pt]{article}
\usepackage[hmargin=1in,vmargin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{times}
\usepackage{indentfirst}
\usepackage{setspace}
%\doublespacing
\setstretch{1.85}
\newcommand{\MySection}[2]{%
  \normalfont\normalsize\noindent{\bf#1.\hspace{1em}#2}}
\setlength{\parindent}{0.5in}

\begin{document}

\MySection{A}{Summary Description}

% Overview

Under this proposal, I seek support to write a manuscript for professional
publication based on a set of completed experiments.  This proposed project
will allow me to finish off one stage of a longer project and lay the
groundwork for the next stage.

% My Background and Topic

My background is in cognitive psychology.  This field seeks to analyze
human thought by breaking it into a set of separate systems, each of which
process information in some way.  The focus of my research is on attention
and short-term memory, the processes that select relevant information and
store it briefly while it is relevant to the task at hand.

% The project

The current proposal seeks to advance my research on how attention switches
between different sources of information.  We do this regularly in our
daily activities.  For example, when we are driving, we regularly look away
from the traffic in front of us to check a mirror or glance at the
dashboard.  My colleagues and I have developed a technique that allows us
to precisely measure the recovery time following such a shift in attention.
We have conducted many experiments to test the validity and reliability of
the technique, and have found that it takes roughly 40 milliseconds (0.04
seconds) to recover after an attentional shift.

% This specific proposal

Under this proposal, I will write a manuscript based on the completed
experiments and develop the next stage of this project.  The experiments
were intended to test the technique and establish a baseline measure of
recovery time.  The results need to be published to communicate the
technique to other researchers and establish it in the literature. The next
stage of this project will involve applying the technique to situations in
which other distracting tasks are also being performed simultaneously.

This next stage is relevant to real-world tasks.  To continue the earlier
example, while driving and switching attention between various important
sources of information, many people also pay attention to less important
things such as navigation systems or cell phone conversations.  A great
deal of research has established that such distracting tasks can be
dangerous, but nobody has yet established how they affect attention.  My
technique presents a means to investigate a specific aspect of attention
that may be affected by distracting tasks.

\MySection{B}{Methods, Procedures, and Student Involvement}

The proposed project focuses on writing, not running studies.
Nevertheless, I will summarize the methods used in the completed
experiments.  These studies used standard experimental psychology
procedures: that is, we developed a computerized task similar to a video
game, then have subjects complete the task while we measure various aspects
of their performance.

The technique we used is based on a standard experimental task called the
multiple object tracking (MOT) task.  In it, a set of identical objects
move randomly around a computer display.  People must keep track of a
subset of those objects called targets, despite the fact that targets look
identical to all other stimuli.  This is a demanding task because any lapse
in attention will result in lost targets.  In our version of the technique,
all the objects disappear for about a tenth of a second, then reappear.  We
can determine how long it takes people to recover from the disappearance by
measuring their performance at various intervals after reappearance.

CSUEB students have been involved at several stages of this project.
Students in my PSYC 3100 section in Fall 2008 helped to run a pilot version
of this experiment.  Melanie Johnson, who graduated last year with a
B.A. in Psychology from CSUEB, collected much of the data and will be a
co-author on the manuscript.  The follow-up projects will also be completed
with the assistance of CSUEB Psychology majors.

\MySection{C}{Timetable}

I plan to develop a final control experiment in Summer 2011 and run it
during Fall quarter.  I plan to complete the proposed project in the Winter
quarter of 2012.  I anticipate the following approximate timetable:

\begin{center}
  \begin{singlespace}
    \begin{tabular}{ll}\hline
      January & Finish analyzing all data \\
      January--February & Write draft \\
      March & Revisions and feedback from co-authors \\
      End of March & Submit to journal \\\hline
    \end{tabular}
  \end{singlespace}
\end{center}

\MySection{D}{IRB Status}

The experiments in this proposal were conducted on human subjects.  The
project was reviewed by the CSUEB IRB and deemed exempt from review (IRB
project title: ``Mechanisms of Visual Attention and Short-Term Memory'').
The project was originally reviewed in July, 2008, and its most recent
continuation review is valid until July 14, 2011.

\MySection{E}{Relationship to Prior and Future Work}

The work I plan to complete under the proposed project will allow me to
finish off work that was originally begun during my postdoctoral research
fellowship and finished at CSUEB.  The proposal would allow me to complete
this stage of the project and begin working on the next stage.

\end{document}
